Exposing Bugs in JavaScript Engines through Test Transplantation and Differential Testing

### 2020-06-12 paper/paper.tex
fix bug number in discussion

\vspace{1ex}\noindent\textbf{Issue \#18,
  Table~\ref{tab:test-transplantation-bugs}.}\Mar{$\leftarrow$ isto
  esta errado! A tabela diz que eh Chakra}  The code snippet below
shows the test input we used to reveal a bug in \jsc.

>>>>

\vspace{1ex}\noindent\textbf{Issue \#19,
  Table~\ref{tab:test-transplantation-bugs}.} The code snippet below
shows the test input we used to reveal a bug in \jsc.
